---
title: "Implementation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Implementation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rsixer)
```

## Technical Implementation Details

### Shiny Integration

All R6 modules maintain full compatibility with Shiny's module system:

1.  **UI Methods**: Return valid Shiny tag objects suitable for embedding in any UI
2.  **Server Methods**: Use `shiny::moduleServer(private$id, ...)` internally
3.  **Namespace Functions**: Store and use `shiny::NS()` in private field
4.  **Reactives**: Return reactive values/expressions directly from `$server()` methods

### Data Pipeline Architecture

```         
ModInputs$server() → inputs_r (reactive list)
                       ↓
ModOutputs$server(inputs_r) → prices_r (eventReactive on fetch)
                                ↓
                            returns_r (reactive computation)
                                ↓
                            perf_r (reactive summary)
                                ↓
ModDownload$server(inputs_r, perf_r) → handles download
```

### Logging Architecture

```         
rsixer/app                 # App-level events
├── rsixer/inputs        # Input module events
├── rsixer/outputs       # Output module events
│   ├── rsixer/tooltip   # Tooltip dispatch
│   └── rsixer/hoverinfo # Hover-info rendering
└── rsixer/download      # Download module events
```

------------------------------------------------------------------------

## Package Configuration

### DESCRIPTION File

Key sections:

-   **Package**: `rsixer`
-   **Version**: `0.1.0`
-   **Type**: Package with Shiny application
-   **Imports**: R6, shiny, bslib, dplyr, tidyquant, reactable, logger, etc.
-   **Suggests**: testthat, knitr
-   **Config/testthat/edition**: 3 (modern testthat)
-   **Roxygen2**: Configured for documentation generation

### renv.lock (Dependencies)

Pins exact versions for reproducibility: - R 4.5.0 - 30+ packages with specific versions